---
title: "Class 2 HW - Student"
output: html_notebook
---
#Setting up the below based off Lab 3 in order to work off actual data regardless of requirements. 


```{r, eval = FALSE}
#Clearing libraries to prevent errors

detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)


}

detachAllPackages()
```


From: (https://emilhvitfeldt.github.io/ISLR-tidymodels-labs/index.html)

Note: We are continuing with the Boston data set but...https://medium.com/@docintangible/racist-data-destruction-113e3eff54a8

```{r, set.seed(1234)}
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, echo = FALSE, include= FALSE, warning = FALSE, message = FALSE}
#' <!-- ####################################################################################################### -->
#' <!-- ####################################################################################################### -->
#' <!-- ##################################LOADING PACKAGES##################################################### -->

#tryCatch(require(pacman),finally=utils:::install.packages(pkgs='pacman',repos='http://cran.r-project.org'));
#require(pacman)

#' <!-- ##if the above doesn't work, use this code## -->
#' <!-- ##tryCatch -->
#' <!-- #detach("package:pacman", unload = TRUE) -->
#' <!-- #install.packages("pacman", dependencies = TRUE) -->
#' <!-- # ## install.packages("pacman") -->

pacman::p_load(broom,
               corrr,
               dials,
               dplyr,
               factoextra,
               ggplot2,
               glmnet,
               infer,
               ISLR,
               kernlab,
               kknn,
               klaR,
               MASS,
               mclust,
               modeldata,
               paletteer,
               parsnip,
               patchwork,
               proxy,
               purrr,
               randomForest,
               readr,
               recipes,
               rpart,
               rpart.plot,
               rsample,
               scico,
               tibble,
               tidymodels,
               tidyr,
               tidyverse,
               tune,
               vip,
               workflows,
               workflowsets,
               xgboost,
               yardstick,
               conflicted,
               discrim,
               tidylog
               
)

#' <!-- #Loading from GitHub -->
#' <!-- #pacman::p_load_current_gh("trinker/lexicon", "trinker/sentimentr") -->
```

#Okay, running into errors with gzfile(file, mode); UPDATE, rectified upon restarting RStudio

```{r, echo = FALSE, include= FALSE, warning = FALSE, message = FALSE}

#' <!-- #Loading libraries -->

suppressPackageStartupMessages({
library(broom)
library(corrr)
library(dials)
library(dplyr)
library(factoextra)
library(ggplot2)
library(glmnet)
library(infer)
library(ISLR)
library(kernlab)
library(kknn)
library(klaR)
library(MASS)
library(mclust)
library(modeldata)
library(paletteer)
library(parsnip)
library(patchwork)
library(proxy)
library(purrr)
library(randomForest)
library(readr)
library(recipes)
library(rpart)
library(rpart.plot)
library(rsample)
library(scico)
library(tibble)
library(tidymodels)
library(tidyr)
library(tidyverse)
library(tune)
library(vip)
library(workflows)
library(workflowsets)
library(xgboost)
library(yardstick)
library(conflicted)
library(discrim)
library(tidylog)
})

# From: https://rdrr.io/github/Bio302-UiB/data-handling/f/inst/tutorials/using-dplyr/using-dplyr.Rmd
# use purrr::map to iterate over tidylog functions to prevent conflict with dplyr
# map(getNamespaceExports("tidylog"), ~conflict_prefer(.x, "tidylog", quiet = TRUE))

for (f in getNamespaceExports("tidylog")) {
    conflicted::conflict_prefer(f, "tidylog", quiet = TRUE)
}

# Tidylog run through
# From: https://github.com/elbersb/tidylog/blob/master/README.Rmd


```

```{r}
# Setting conflict_prefer
#should be no conflicts in this code
```

# Linear Regression

This lab will go over how to perform linear regression. This will include [simple linear regression] and [multiple linear regression] in addition to how you can apply transformations to the predictors. This chapter will use [parsnip](https://www.tidymodels.org/start/models/) for model fitting and [recipes and workflows](https://www.tidymodels.org/start/recipes/) to perform the transformations.
 
## Libraries

We load tidymodels and ISLR and MASS for data sets.

```{r, message=FALSE}
library(MASS) # For Boston data set; want to make sure I have a reference for how code will actually run
library(tidymodels)
library(ISLR)
```

# 1

Create a `parsnip` specification for a linear regression model.

# HW code
```{r}
lm_spec <- linear_reg() %>% 
  set_mode("regression") %>%
  set_engine("lm") #not technically needed since default is linear regression, but better to be explicit. It is a little silly that we're specifying our linear regression to be a regression analysis using a linear modeling engine.
```

# 2

Once we have the specification we can `fit` it by supplying a formula expression and the data we want to fit the model on.
The formula is written on the form `y ~ x` where `y` is the name of the response and `x` is the name of the predictors.
The names used in the formula should match the names of the variables in the data set passed to `data`. 

Use `lm_spec` to fit the model of `medv` predicted by every predictor variable. Hint: you can use "." to specify every predictor.

# HW code

```{r}
lm_fit <- lm_spec %>%
  fit(medv ~ lstat, data = Boston)
lm_fit
```

# 3

Get a summary of your model using `pluck` and `summary`

# HW code

```{r}
lm_fit %>% 
  pluck("fit") %>% #accessing fit model object created by parsnip
  summary() #getting more detailed information about fit and stats of model
```

# 4

Take a look at `lm_fit` with `tidy`

# HW Code

```{r}
tidy(lm_fit) #return basic parameters of fit object (slope and intercept)
```

# 5

Extract the model statistics using `glance`

#HW code
```{r}
glance(lm_fit) #extract model statistics (significance, fit stats etc)
```

# 6

Get the predicted `medv` values from your model using `predict`

#HW code
```{r}
predict(lm_fit, new_data = Boston) #predicted data for each instance based off model
```


# 7

Bind the predicted columns to your existing data

#HW code

```{r}
bind_cols(
  predict(lm_fit, new_data = Boston), #call predicted values from model
  Boston #add predicted values onto Boston dataframe
) %>%
  select(medv, .pred) #selecting medv and pred data out to compare predicted and actual data
```

# 8

Now, make things easier by just using the `augment` function to do this.

#HW code
```{r}
augment(lm_fit, new_data = Boston) #what we just did but calling whole dataframe rather than selected columns, binds the predicted and residual values to the left side of the data.
```


# 9

Focus specifically on the median value and the `.pred`, then you can select those two columns

#HW code
```{r}
augment(lm_fit, new_data = Boston) %>%
  select(medv, .pred) # going back to calling specifically the median value and predicted values out for easier comparasion. Wow, less code, much wow.
```


# 10

Create a `recipe` with an interaction step between lstat and age

#HW code
```{r}
rec_spec <- recipe(medv ~ ., data = Boston) %>%
  step_interact(~ lstat:age) #specifying recipe step to make new columns that are based off interaction of lstat and age
```

# 11

Create a `workflow` and add your lm_spec model and your rec_spec recipe.

#HW code
```{r}
lm_wf <- workflow() %>% #aggregating information needed for fit and prediction from model based off called objects below
  add_model(lm_spec) %>% #utilizing previous linear regression model
  add_recipe(rec_spec) #utilizing recipe step made in #10
```

# 12

Fit your `workflow`.

#HW code
```{r}
lm_wf %>% fit(Boston) #utilizing fit function from parsnip on workflow made from recipe w/ lstat and age interaction and linear regression model to evaluate model stats
```

